IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex
fix
Missing ref

Existing language-based, coarse-grained IFC
systems~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
allow a sub-computation to temporarily raise the floating-label; after
the sub-computation is done, the floating-label is restored to its
original label. When this occurs, the enforcement mechanism must
ensure that information does not leak to the (less confidential)
program continuation. The presence of exceptions adds yet more
intricacies.  For instance, exceptions should not automatically
propagate from a sub-computation directly into the program
continuation, and, if such exceptions are allowed to be inspected, the
floating-label at the point of the exception-raise must be tracked
alongside the exception value~\cite{Hritcu:2013:YIB:2497621.2498098,
stefan:2012:arxiv-flexiblea, Hedin:2012}.  In contrast, our system
provides the same flexibility and guarantees with no extra checks: tasks
are used to execute sub-computations, but the mere definition of
isolated tasks guarantees that (a) tasks only transfer data to the
program continuation by using inter-task communication means, and (b)
exceptions do cross tasks boundaries automatically.

@@

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.45\textwidth}
\begin{code}
  roundrobin step (it1, it2, ldots)    = it2, ldots, it1
  roundrobin done (it1, it2, ldots)    = it2, ldots
  roundrobin nostep (it1, it2, ldots)  = it2, ldots
  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
\end{code}
\end{minipage} &
\begin{minipage}{.45\textwidth}
\begin{code}
  seq step (it1, it2, ldots)      = it1, it2, ldots
  seq nostep (it1, it2, ldots)    = it1, it2, ldots
  seq done (it)                   = it
  seq done (it1, it2, ldots)      = it2, ldots
  seq box (it1, it2, ldots, itn)  = itn, it1, it2, ldots
\end{code}
\end{minipage}
\end{tabular}
\vspace*{-0.5cm}
\caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}
\label{fig:scheduler}
\end{figure}

>>>>

Existing language-based, coarse-grained IFC
systems~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
allow a sub-computation to temporarily raise the floating-label; after
the sub-computation is done, the floating-label is restored to its
original label. When this occurs, the enforcement mechanism must
ensure that information does not leak to the (less confidential)
program continuation. The presence of exceptions adds yet more
intricacies.  For instance, exceptions should not automatically
propagate from a sub-computation directly into the program
continuation, and, if such exceptions are allowed to be inspected, the
floating-label at the point of the exception-raise must be tracked
alongside the exception
value~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible,Hedin:2012}.
In contrast, our system
provides the same flexibility and guarantees with no extra checks: tasks
are used to execute sub-computations, but the mere definition of
isolated tasks guarantees that (a) tasks only transfer data to the
program continuation by using inter-task communication means, and (b)
exceptions do cross tasks boundaries automatically.

@@

\begin{figure}[t]
\begin{tabular}{ll}
\begin{minipage}{.45\textwidth}
\begin{code}
  roundrobin step (it1, it2, ldots)    = it2, ldots, it1
  roundrobin done (it1, it2, ldots)    = it2, ldots
  roundrobin nostep (it1, it2, ldots)  = it2, ldots
  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
\end{code}
\end{minipage} &
\begin{minipage}{.45\textwidth}
\begin{code}
  seq step (it1, it2, ldots)      = it1, it2, ldots
  seq nostep (it1, it2, ldots)    = it1, it2, ldots
  seq done (it)                   = it
  seq done (it1, it2, ldots)      = it2, ldots
  seq box (it1, it2, ldots, itn)  = itn, it1, it2, ldots
\end{code}
\end{minipage}
\end{tabular}
\vspace*{-0.5cm}
\caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}
\label{fig:scheduler}
\end{figure}
